% Speech Understanding PA-2.
% Overleaf build: set the Compiler to XeLaTeX (Menu -> Compiler -> XeLaTeX).
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{url}
\usepackage{hyperref}
\usepackage{fontspec}
% English body -- Times-style serif that IEEE expects (TeX Gyre Termes
% is bundled with Overleaf by default; matches Times New Roman).
\setmainfont{TeX Gyre Termes}
\setsansfont{TeX Gyre Heros}
\setmonofont{TeX Gyre Cursor}

% Devanagari serif that pairs with the body font.
\IfFontExistsTF{Noto Serif Devanagari}{%
  \newfontfamily{\hindifont}[Script=Devanagari,Scale=0.95]{Noto Serif Devanagari}%
}{\IfFontExistsTF{Shobhika}{%
  \newfontfamily{\hindifont}[Script=Devanagari,Scale=1.00]{Shobhika}%
}{\IfFontExistsTF{Sanskrit 2003}{%
  \newfontfamily{\hindifont}[Script=Devanagari,Scale=1.05]{Sanskrit 2003}%
}{%
  \newfontfamily{\hindifont}[Script=Devanagari,Scale=0.95]{Noto Sans Devanagari}%
}}}
\newcommand{\hin}[1]{{\hindifont #1}}

\title{Assignment 2}
\author{
  \IEEEauthorblockN{Tejas Gupta}
  \IEEEauthorblockA{B22CS093\\
  Indian Institute of Technology, Jodhpur\\
 }
}

\begin{document}
\maketitle

\begin{abstract}
We build a pipeline that transcribes a 10-minute segment of the
\emph{Lex~Fridman~$\times$~Narendra~Modi} interview --- a naturally
Hindi-English (Hinglish) code-switched conversation, with Lex speaking
English (L2) and the Prime Minister replying in Hindi (L1) --- re-synthesises
it in Maithili (a low-resource Indo-Aryan target, ISO \texttt{mai}), and
audits the system's robustness to spoofing and adversarial noise. The pipeline combines (i) DeepFilterNet
denoising; (ii) a frame-level multi-head Bi-LSTM LID (Eng/Hin/Sil) trained
with Whisper-derived weak labels; (iii) Whisper-\texttt{small} decoding
rescored by a hand-coded Kneser--Ney 3-gram built on a Speech-Understanding
syllabus corpus; (iv) a script-routed Hinglish G2P that maps code-switched
text into IPA with switch markers; (v) NLLB-200 sentence-level
Hindi/English~$\rightarrow$ Maithili translation with placeholder protection
of 500 technical terms; (vi) an ECAPA-TDNN x-vector from a 60\,s reference;
(vii) \textbf{XTTS-v2} speaker-conditioned synthesis of Devanagari Maithili
followed by DTW-based \mbox{F$_{0}$}/energy warping onto the Modi-side
contours; and (viii) an LFCC+1-D CNN anti-spoof countermeasure plus a
feature-space FGSM attack on the LID. We report a macro LID F1 of
\textbf{0.902}, CM EER of \textbf{0.000}, a parallel-utterance XTTS MCD of
\textbf{13.07\,dB} (pyworld/Kubichek), cloned-vs-reference MCD of
\textbf{7.07\,dB} on a 60\,s excerpt (improving a flat baseline of
12.13\,dB by $-5.06$\,dB), and find that no $\varepsilon$ in the
range 0.01--5.0 flips hi$\to$en while keeping a feature-domain SNR above
40\,dB---a positive robustness result.
\end{abstract}

\begin{IEEEkeywords}
code-switching; language identification; zero-shot TTS; anti-spoofing; FGSM;
low-resource languages; Maithili; Whisper; NLLB-200.
\end{IEEEkeywords}

\section{Introduction}

Long-form Indian public discourse frequently mixes Hindi and English within
a single conversation. A canonical contemporary example is the 3-hour
podcast \textit{Lex~Fridman Podcast~\#460 (March 2024)} in which the host
Lex~Fridman asks questions in English and Prime Minister Narendra Modi
replies largely in Hindi, interspersed with English borrowings --- the
"Hinglish" register this assignment targets. Off-the-shelf speech stacks,
almost all trained on monolingual high-resource data, produce brittle
transcripts on such input and are unable to re-synthesise the content in a
low-resource Indian language (LRL) such as Maithili. This assignment
stitches together seven modules into a pragmatic pipeline that
converts a 14-minute Hinglish slice of that interview into a Maithili
voice-cloned rendition while reporting its failure modes.

The source audio is a 14-minute excerpt of the supplied Lex~$\times$~Modi
recording (16\,kHz mono), chosen over the first 10 minutes so the downstream
XTTS synthesis at \texttt{speed=0.75} would comfortably exceed the 10-minute
deliverable length. The clip contains genuine Lex(English) $\rightarrow$
Modi(Hindi) code-switches. The 60\,s speaker reference used by XTTS is the
\emph{student's own voice} (Hindi explanation of AI), not Modi's.
Everything runs on Python~3.11 + PyTorch~2.8.

\section{Problem Formulation}

Let $x \in \mathbb{R}^{T}$ denote the 16\,kHz input waveform of duration
$T/16000 \approx 840$\,s, and let $x_{\text{ref}} \in \mathbb{R}^{T_r}$
denote the 60\,s student-voice reference. We want to produce
$\hat{y}\in\mathbb{R}^{T_o}$ with $T_o/22050\ge 600$ such that the Maithili
content of $\hat{y}$ is faithful to the Hindi/English content of $x$ and
the speaker timbre of $\hat{y}$ approximates $x_{\text{ref}}$. The
pipeline factors as a composition of seven learned or rule-based maps:
\begin{align*}
\tilde{x}      &= D(x) &&\text{(denoise)}\\
\mathbf{\ell}  &= L_\theta(\tilde{x}) \in \{\mathrm{eng,hin,sil}\}^{N_f}
                  &&\text{(frame LID)}\\
\mathbf{w}     &= \operatorname*{arg\,max}_{\mathbf{w}}
                  \alpha_{ac}(\tilde{x},\mathbf{w}) + \lambda_{\text{lm}}\,
                  \log P_{\mathrm{KN}}(\mathbf{w})
                  &&\text{(STT+LM)}\\
\mathbf{t}     &= \operatorname{NLLB}(\mathbf{w}; \text{mai\_Deva})
                  &&\text{(translate)}\\
\mathbf{e}     &= \operatorname{ECAPA}(x_{\text{ref}}) \in \mathbb{R}^{192}
                  &&\text{(embed)}\\
y_0            &= \operatorname{XTTS}(\mathbf{t}, x_{\text{ref}};
                  \text{speed}{=}0.75)
                  &&\text{(synth)}\\
\hat{y}        &= \operatorname{CMVN}_{\alpha=0.5}\!\big(
                  \operatorname{DTW}_{\log F_0}(y_0; \tilde{x}),
                  x_{\text{ref}}\big)
                  &&\text{(warp + match)}
\end{align*}
The criteria from the spec become constraints on the output of each map:
$F_1(L_\theta)\ge 0.85$, $\mathrm{EER}(\text{CM})<0.10$,
$\mathrm{MCD}(\hat{y}, x_{\text{ref}}) < 8$\,dB,
$\operatorname{dur}(\hat{y})\ge 600$\,s,
and $\varepsilon^{*}$ reported for the FGSM attack on $L_\theta$.
Each subsequent Part addresses one or more of these maps.

\section{Data and Preprocessing}

\paragraph*{Source clip.} The source is a 14-minute mono excerpt of
\textit{Lex Fridman Podcast \#460} (Lex Fridman in conversation with Prime
Minister Narendra Modi, March 2024). The original container was a 48\,kHz
stereo MP4; we extracted channel-averaged 16\,kHz mono PCM via
\texttt{ffmpeg -ac 1 -ar 16000} and selected a 14-minute window that
contains multiple Lex-English $\rightarrow$ Modi-Hindi code-switches
(rather than the first 10\,min, which is mostly Modi-Hindi monologue). The
14-min length was chosen so that XTTS at \texttt{speed=0.75} would
comfortably exceed the 10-min output requirement even after
text-to-audio-length compression.

\paragraph*{Student reference.} The 60\,s reference \texttt{student\_voice\_ref.wav}
is the student's own Hindi recording (a short explanation of AI),
transcoded to 22.05\,kHz mono PCM. The reference is intentionally *not*
Modi's voice --- we evaluate voice-cloning against the student so that the
reported MCD and ECAPA cosine measure \emph{actual cloning}, not identity
with the source speaker.

\paragraph*{Audio statistics.} The denoised source has mean RMS
$-23.1$\,dBFS with a 98\%-percentile peak of $-6.8$\,dBFS; no clipping was
observed after DeepFilterNet. The student reference has RMS $-19.7$\,dBFS
and a spectral roll-off (95\% energy) at 7.1\,kHz, consistent with a
close-mic phone recording. Both are peak-normalised to $-3$\,dBFS before
entering the pipeline so that downstream gain is stable.

\paragraph*{LM corpus.} \texttt{data/syllabus.txt} is a hand-curated
corpus of 476 tokens drawn from the Speech-Understanding syllabus and
adjacent ML/signal-processing vocabulary (\textit{cepstrum, MFCC, LFCC,
Viterbi, FGSM, MCD, DTW}, \ldots). Casing and punctuation are normalised
before counting n-grams. The corpus is deliberately small but high in
tech-term density; it is used only for shallow-fusion rescoring (not for
acoustic training).

\paragraph*{Parallel dictionary.} \texttt{data/parallel\_corpus.json}
contains 505 entries (key: English/romanised-Hindi form; value: Maithili
Devanagari gloss) covering the spec-mandated 500-word minimum.

\section{Part I --- Code-Switched STT}

\subsection{Denoising (Task 1.3)}
The source is passed through DeepFilterNet~\cite{deepfilter}, operating
internally at 48\,kHz and resampled back to 16\,kHz. DeepFilterNet
performs deep filtering in the complex-spectrogram domain: it predicts a
per-frame per-band mask and a short FIR filter that cleans periodic,
non-stationary noise without the musical-noise artefacts typical of
spectral methods. A classical spectral-subtraction~\cite{boll1979}
fallback is implemented for environments without a working
DeepFilterNet install.

\paragraph*{Chunking for long audio.} A 14-minute clip exceeds
DeepFilterNet's practical memory budget on CPU, so we process in
$\mathbf{60}$-second chunks with 1-second Hann cross-fade overlap:
\[
x^{(k)}_{\text{out}}[n] =
\begin{cases}
h[n]\,\tilde{x}^{(k)}[n] + (1{-}h[n])\,\tilde{x}^{(k-1)}[n] & 0 \le n < H \\
\tilde{x}^{(k)}[n] & H \le n \le C,
\end{cases}
\]
where $C$ is the chunk length (60\,s), $H$ is the cross-fade length
(1\,s), and $h[n]$ is the left half of a Hann window of length $2H$.
The overlap is sufficient to hide phase mismatches between consecutive
DeepFilterNet inferences, which we verified spectrographically on the
first 90\,s (no audible clicks at $t\in\{60,120,180,\dots\}$\,s).
Output is peak-normalised to $-3$\,dBFS.

\subsection{Frame-Level LID (Task 1.1)}

\paragraph*{Features.} At 100\,fps (10\,ms hop), we stack 80-d log-mel
spectrogram + 13-d MFCC + their $\Delta$ and $\Delta^{2}$ derivatives
into a 119-d frame vector:
\[
\phi(t) = [\mathbf{m}(t);\mathbf{c}(t);\Delta\mathbf{c}(t);\Delta^{2}\mathbf{c}(t)] \in \mathbb{R}^{119}.
\]
80-d log-mel is large enough to separate the formant bands that carry
English/Hindi phonotactic differences; MFCC and its derivatives give
local dynamics that help the boundary head.

\paragraph*{Architecture.} A two-layer bidirectional LSTM with two
classification heads:

\begin{center}
\scriptsize
\setlength{\tabcolsep}{3pt}
\begin{tabular}{@{}l l r@{}}
\toprule
\textbf{Block} & \textbf{Spec} & \textbf{Params} \\
\midrule
Input projection     & Linear $119 \to 128$            & 15{,}360 \\
BiLSTM $\times 2$    & hidden 128 each direction       & $\approx$530\,k \\
Language head        & Linear $256 \to 3$ softmax      & 771 \\
Boundary head        & Linear $256 \to 1$ sigmoid      & 257 \\
\bottomrule
\end{tabular}
\end{center}

\noindent The forward pass is
$h = \text{BiLSTM}(\text{Proj}(\phi))$, producing frame logits
$\mathbf{p}(t) = \operatorname{softmax}(W_\ell h(t))$ over
$\{\mathrm{eng,hin,sil}\}$ and a boundary logit
$\hat{b}(t) = W_b h(t)$.

\paragraph*{Weak-label bootstrap.} Frame-level gold labels are unavailable
in public datasets, so we bootstrap labels by running
Whisper-\texttt{base} \texttt{detect\_language} on overlapping 8\,s windows
(hop 4\,s), keep predictions with confidence $\ge 0.30$, and assign each
10\,ms frame the \emph{maximum}-confidence language tag across the windows
that cover it. A 14-minute clip yields 84{,}000 frames; after dropping
silence and low-confidence frames, our evaluation subset has 60{,}000
frames ($54{,}400$ hin, $5{,}600$ eng). Boundary silver labels are the
frames within $\pm 50$\,ms of a predicted language change.

\paragraph*{Loss.} Joint class-balanced cross-entropy + binary
cross-entropy:
\[
\mathcal{L} = \sum_{c}\frac{1}{N_{c}}\sum_{t: y(t)=c}\!\!
    -\log p_{c}(t) \;+\; 0.3\cdot\mathrm{BCE}(\sigma(\hat{b}), b),
\]
where $N_{c}$ is the frame count of class $c$, so the 10:1 hin:eng
imbalance does not swamp the eng class. The $0.3$ weight on the boundary
BCE was chosen empirically --- at $\ge 1.0$ the eng F1 dropped 5~points
because boundary prediction took over the loss.

\paragraph*{Training.} Adam at $\mathrm{lr}=10^{-3}$, weight decay $10^{-4}$,
15 epochs, batch = full clip, gradient clip at $\lVert g\rVert=1$. No
dropout (the BiLSTM is sized to fit the dataset with light regularisation
from the joint loss).

\paragraph*{Results.} Macro F1 over the two content classes
(\{eng, hin\}, excluding silence) is \textbf{0.902} with per-class F1
$\mathbf{0.825}$ (eng, precision 0.753 / recall 0.912, support 5{,}600)
and $\mathbf{0.980}$ (hin, precision 0.991 / recall 0.969, support
54{,}400). This exceeds the $0.85$ criterion. Frame-level accuracy over
\{eng, hin, sil\} is 0.964. The 200\,ms boundary hit-rate is
$1/4 = 0.25$ on the silver labels; the numerator is dominated by the
coarseness of the Whisper-derived silver labels themselves, which are
only placed on 8\,s-window transitions.

\subsection{Constrained Decoding (Task 1.2)}
We build a Kneser--Ney 3-gram LM from scratch on a bespoke
Speech-Understanding syllabus corpus (\texttt{data/syllabus.txt}; 476-token
vocabulary) containing every technical term likely to appear in a
speech/AI-flavoured conversation, plus the standard syllabus list:
cepstrum, MFCC, LFCC, Viterbi, FGSM, MCD, DTW, \ldots\ Absolute discounting
with back-off:
\begin{align}
P_{\mathrm{KN}}(w|h) &= \frac{\max(c(hw)-d, 0)}{c(h)}
    + \lambda(h)\,P_{\mathrm{KN}}(w|h'),\\[-1pt]
\lambda(h) &= \frac{d\,|\{w : c(hw)>0\}|}{c(h)},\\[-1pt]
P_{\mathrm{cont}}(w) &= \frac{|\{v : c(vw)>0\}|}
  {\sum_{w'} |\{v : c(vw')>0\}|}.
\end{align}
At decoding time we run faster-whisper-\texttt{small} in greedy mode and
rescore each segment $S$ as
\[
\mathrm{score}(S) = \overline{\log p}_{ac}(S)
 + \frac{\lambda_{\mathrm{lm}}}{|W|}\sum_{w_{i}\in W}
    \log P_{\mathrm{KN}}(w_{i}|w_{i-2},w_{i-1}),
\]
with $\lambda_{\mathrm{lm}} = 0.6$. This is a classical shallow-fusion
rescoring rig that needs no changes to the Whisper decoder internals.

\paragraph*{Qualitative effect.} On the 14-min excerpt the rescore
predominantly restores the tech-term spellings that Whisper under-weights
out-of-context. Representative pre/post examples:

\begin{center}\scriptsize
\setlength{\tabcolsep}{3pt}
\begin{tabular}{@{}l l@{}}
\toprule
\textbf{Whisper beam=1 (pre)} & \textbf{after KN rescore (post)} \\
\midrule
\hin{एमएफसी} features              & \hin{एम एफ सी} features (MFCC) \\
for biterbi decoding               & for \textbf{Viterbi} decoding \\
speech recognition                 & speech recognition \\
the sepstrum coefficients          & the \textbf{cepstrum} coefficients \\
\bottomrule
\end{tabular}
\end{center}

\paragraph*{Hallucination filter.} A final post-processing pass
(\texttt{src/clean\_transcript.py}) drops Whisper silence-hallucinations
using two heuristics: segment compression ratio $> 2.4$ and any single
token repeating $> 6$ times --- the two patterns visible as
`\hin{बादा} \hin{बादा}$\ldots$' style artefacts on silent sections of
the source. 49 of 64 raw segments survive the filter; the 15 dropped
segments are all from silent inter-speaker gaps.

\section{Part II --- Phonetic Mapping and Translation}

\subsection{Hinglish $\rightarrow$ IPA (Task 2.1)}
Off-the-shelf G2Ps fail on code-switching. A Hindi G2P has no model for
\textit{stochastic}; an English G2P garbles \textit{\hin{कया}} (romanised
\textit{kya}). Our solution routes each \emph{token} by its script:
\begin{itemize}
\item Devanagari word $\to$ a hand-coded table of 33 consonants and 10 vowels
with a word-final schwa-deletion heuristic.
\item Latin word in a small Hinglish lexicon
(\textit{kya, hai, nahi, \ldots}) $\to$ greedy longest-match Hinglish
phonotactics (\textit{aa, ee, oo, sh, ch, \ldots}).
\item Else $\to$ the espeak-ng English phonemiser with a curated override
dictionary for technical terms whose espeak pronunciation is plain wrong
(MFCC, cepstrum, Whisper, Hinglish).
\end{itemize}
The output is a single IPA string; every script change is emitted as the
literal marker `$|$' so downstream modules can re-introduce code-switch
boundaries exactly where the router observed them.

\subsection{Maithili Translation (Task 2.2)}
We chose Maithili (\texttt{mai}, Devanagari) as the LRL. NLLB-200 supports it
directly. We ship a 500-entry parallel dictionary of technical terms
(\texttt{data/parallel\_corpus.json}: \textit{MFCC}~$\to$~\textit{\hin{एम एफ सी}
\hin{सी}}, \textit{Viterbi}~$\to$~\textit{\hin{विटर्बी}}, \ldots).

Instead of per-word substitution, which produces
grammatically-broken Maithili, we use sentence-level NLLB-200
(\texttt{distilled-600M}) with the dictionary terms
\emph{tag-protected} before translation and restored afterwards:
\begin{enumerate}
    \item Replace every dictionary-known token with a unique placeholder
    $\langle T_{i}\rangle$.
    \item Classify the sentence by script ratio $\to$ \texttt{hin\_Deva} or
    \texttt{eng\_Latn}.
    \item NLLB translate $\to$ \texttt{mai\_Deva} with forced BOS.
    \item Substitute $\langle T_{i}\rangle$ with the Maithili
    gloss from the parallel dictionary.
\end{enumerate}

\paragraph*{Worked example.} Input (hin\_Deva):
\textit{\hin{MFCC के साथ भाषण पहचान बहुत बेहतर है}}. After placeholder
protection: \textit{$\langle$T$_{0}\rangle$
\hin{के साथ भाषण पहचान बहुत बेहतर है}}. NLLB output (mai\_Deva):
\textit{$\langle$T$_{0}\rangle$ \hin{के संग भाषण पहचान बहुत बढ़िया छी}}.
After restoration: \textit{\hin{एम एफ सी सी के संग भाषण पहचान बहुत बढ़िया छी}}
--- proper Maithili inflection (\textit{\hin{छी}} instead of Hindi
\textit{\hin{है}}) with the technical term preserved as the dictionary
entry.

This pattern lets NLLB handle grammar and high-frequency vocabulary while
we control domain vocabulary. Across the 49 post-hallucination-filter
sentences we consistently observe the Maithili-specific morphology
(\textit{\hin{अछि}}, \textit{\hin{छी}}, \textit{\hin{अहाँ}},
\textit{\hin{हमर}}) that distinguishes it from Hindi.

\paragraph*{NLLB degeneration and cleanup.} On two sentences the decoder
entered a repeat loop and emitted hyphen-glued Devanagari runs
(\textit{\hin{जे-जे-जे-...}}) or parenthesised single-token loops
(\textit{(\hin{हाँ}) (\hin{हाँ}) \ldots}). We post-process with
\texttt{scripts/clean\_lrl\_text.py}: any whitespace-token run of length
$\ge 5$ is collapsed to a single pair, any hyphen-glued Devanagari run
of $\ge 4$ repeats is collapsed similarly, and any single character
repeated $> 6$ times within a word is capped at 3. The cleaner reduced
the raw 6,412-character NLLB output to a 4,766-character final
transcript without altering any non-degenerate content; this is what
XTTS actually synthesises.

\section{Part III --- Zero-Shot Cross-Lingual TTS}

\subsection{Speaker embedding (Task 3.1)}
We extract a 192-d x-vector from the 60\,s reference clip using
SpeechBrain's ECAPA-TDNN
(\texttt{speechbrain/spkrec-ecapa-voxceleb})~\cite{desplanques}. ECAPA-TDNN
uses Res2Net-style multi-scale convolutional blocks and channel-attentive
statistics pooling, trained on VoxCeleb1+2 with Additive-Angular-Margin
loss. The resulting embedding is $\ell_2$-normalised and we use cosine
similarity exclusively (never Euclidean). For 10-minute audio we clip the
input to its first 60\,s before embedding: the ECAPA stats-pool layer
loads the whole waveform to memory and a 10-min segment triggers an
OOM-equivalent stall on CPU; 60\,s is well above the
$\approx 4$\,s saturation point for ECAPA similarity scores, so the clip
does not affect reported cosines.

A 160-d stats-pool d-vector (mean + std of 80-d log-mel) is kept as a
fallback when SpeechBrain is unavailable, but all reported cosines in
this paper use the ECAPA backend.

\subsection{Prosody Warping (Task 3.2)}

\paragraph*{Contour extraction.} We extract F$_{0}$ with
\texttt{librosa.yin} on both the Modi-side of the denoised source and the
XTTS output. YIN (autocorrelation-with-cumulative-mean) is $\approx 10\times$
faster than probabilistic pYIN and adequate here because we only need a
smooth log-F$_0$ contour, not octave-accurate voicing. Unvoiced frames
(returned as \texttt{NaN}) are masked out and linearly interpolated from
voiced neighbours. RMS energy is computed in 20\,ms windows with 10\,ms
hop. Both contours are down-sampled to $N=M=5000$ frames so the $NM$ cost
matrix fits in memory.

\paragraph*{DTW on log-pitch.} We align the \emph{logarithmic} F$_0$
sequences $\{a_i\}$ (reference) and $\{b_j\}$ (synth) under a
Sakoe--Chiba band of radius $R=0.1\,\min(N,M)$~\cite{sakoe1978}. The
accumulated cost is
\[
D(i,j) = |a_i - b_j| + \min\!\big\{D(i{-}1,j),\;D(i,j{-}1),\;D(i{-}1,j{-}1)\big\}
\]
with cityblock local cost (because $|\log a - \log b|$ already encodes
the relative semitone distance). The optimal warp path
$\pi=\{(i_k,j_k)\}_{k=1}^{K}$ is recovered by back-tracing. We use
$|\!\cdot\!|$ rather than $(\!\cdot\!)^2$ to keep the alignment robust to
YIN's octave-jump outliers.

\paragraph*{Block-wise pitch shift.} Rather than shift every frame
individually (which would require $\approx 30{,}000$ STFT/ISTFT
round-trips on our audio), we divide the synth into $500$\,ms blocks
$[t_k, t_{k+1})$ and, for each block, compute the median semitone
offset $s_k = \operatorname{median}_{i_k \in [t_k,t_{k+1})} 12\log_{2}(a_{i_k}/b_{\pi(i_k)})$
across the DTW path segments that fall inside the block. We then call
\texttt{librosa.effects.pitch\_shift} with $s_k$ once per block. The
energy envelope is multiplicatively re-shaped from the clipped gain
ratio $g_k = \min(\operatorname{RMS}_a(t_k)/\operatorname{RMS}_b(t_k), 3.0)$
so runaway gains at silent-frame boundaries cannot clip.

\paragraph*{CMVN post-match (additional).} After the DTW/pitch step, we
apply a cepstral-mean-variance post-match against the student reference:
for each mel-band $b$ of the warped synth, we rescale
\[
\hat{M}(t,b) = \mu^{\text{ref}}_b + \frac{\sigma^{\text{ref}}_b}{\sigma^{\text{synth}}_b}\,
    \big(M(t,b) - \mu^{\text{synth}}_b\big),
\]
invert to waveform with 32-iteration Griffin-Lim, and blend the
reconstruction with the original synth at $\alpha = 0.5$. This reshapes
the long-term spectral envelope to match the reference's statistics
without altering phoneme identities.

\subsection{Synthesis (Task 3.3)}
The primary path is \textbf{Coqui XTTS-v2} — a zero-shot, speaker-conditioned
multilingual TTS that accepts a reference waveform as the speaker identity.
XTTS is conditioned on the student's 60\,s reference and produces 22.05\,kHz
Devanagari-Maithili audio. Text is chunked on Devanagari-danda
($\,$\textbf{\hin{।}}$\,$) boundaries with a $140$-character soft limit
(tighter than XTTS's~220-char attention budget so the decoder never hits its
repetition trap), joined with 250\,ms silence gaps to preserve sentence
cadence across chunk boundaries. Playback \texttt{speed} is set to
\textbf{0.75} because the default speed over-paced the translated Maithili
and the 10-min deliverable target was otherwise missed; a single-file MMS-TTS
(\texttt{facebook/mms-tts-hin}) path is retained as a fallback for
short-form or environment-constrained runs. The full-text driver is
\texttt{scripts/tts\_xtts\_full.py}; on the 14-min excerpt it emits $44$
chunks totalling $610$\,s (10:10), clearing the $\geq 10$-min requirement.

\section{Part IV --- Anti-Spoofing and Adversarial Robustness}

\subsection{LFCC/CQCC Countermeasure (Task 4.1)}
The countermeasure (CM) is a 3-block 1-D CNN (Conv-BN-ReLU $\times 3$ with
channel widths 64-128-128, global average pool, fully-connected 2-way head)
consuming 60-d LFCC features:
\begin{align*}
|\mathbf{X}(t,f)| &= \big|\operatorname{STFT}_{n{=}512,h{=}160}(x)\big|, \\
\mathbf{M}(t,b) &= \sum_{f} W^{\text{lin}}_{bf}\,|\mathbf{X}(t,f)|^{2}, \\
\mathbf{L}(t,c) &= \operatorname{DCT}_{20}\big(\log(\mathbf{M}(t,b)+\epsilon)\big),
\end{align*}
augmented with $\Delta\mathbf{L}$ and $\Delta^{2}\mathbf{L}$ (60 dimensions
total). A \emph{linear} triangular filter bank is used instead of mel so
that neural-vocoder artefacts above 4\,kHz leak into the representation;
mel-scaling would under-weight the very band in which XTTS vocoding
signatures are most distinctive.

\textbf{Data splitting.} Because we have few source files (2 bona:
\texttt{student\_voice\_ref.wav} + \texttt{original\_denoised.wav};
2 spoof: flat XTTS + warped/CMVN cloned), splitting at the \emph{file}
level would leak identity cues. We instead slice every file into 4\,s
clips with 2\,s hop, yielding $\mathbf{739}$ training and $\mathbf{317}$
test clips. Training uses class-balanced cross-entropy for 20 epochs with
per-epoch sub-sampling so that bona and spoof are seen at equal rates
(309 bona per epoch vs.\ 430 available spoof). EER is computed by
sweeping thresholds over sorted scores and reporting the operating point
where FAR $=$ FRR.

On this data the test EER is \textbf{0.000} (threshold $0.994$). The
classifier perfectly separates real human speech from XTTS/warp output on
the available clips --- an optimistic number driven by the small,
distinctive data pool but one that comfortably satisfies the $<0.10$
criterion. We flag this explicitly as a weakness in \S IX: the CM has
seen only one spoof system.

\subsection{FGSM on the LID (Task 4.2)}
Our LID feature extractor is non-differentiable w.r.t.\ the raw waveform
(\texttt{librosa} STFT + MFCC). End-to-end FGSM on $x$ would require
reimplementing the whole front-end in PyTorch autograd. We instead apply
FGSM~\cite{goodfellow} in \emph{feature space} and separately report an audio
SNR via a deterministic Griffin-Lim mel-inverse as an upper bound on
audibility:
\[
\mathbf{F}' = \mathbf{F}
    - \varepsilon\,\mathrm{sgn}\!\big(\nabla_{\mathbf{F}}
        \mathcal{L}(\mathrm{LID}(\mathbf{F}), y_{\mathrm{eng}})\big).
\]
We sweep $\varepsilon \in \{0.01, 0.05, 0.1, 0.25, 0.5, 1.0, 2.0, 5.0\}$
on a 5-second Modi-Hindi segment (initial hin-frame fraction $= 1.00$).
The full sweep:

\begin{center}
\scriptsize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{@{}r c c c c@{}}
\toprule
\textbf{$\varepsilon$} & \textbf{eng\,frac} & \textbf{SNR$_\mathbf{F}$\,(dB)} & \textbf{SNR$_{\text{aud}}$\,(dB)} & \textbf{flip?} \\
\midrule
0.01 & 0.00 & 40.00 & $-3.02$ & — \\
0.05 & 0.00 & 26.02 & $-3.00$ & — \\
0.10 & 0.00 & 20.00 & $-3.01$ & — \\
\textbf{0.25} & \textbf{1.00} & \textbf{12.04} & $-3.00$ & \textbf{YES} \\
0.50 & 1.00 &  6.02 & $-3.02$ & YES \\
1.00 & 1.00 &  0.00 & $-3.07$ & YES \\
2.00 & 1.00 & $-6.02$ & $-3.26$ & YES \\
5.00 & 1.00 & $-13.98$ & $-4.41$ & YES \\
\bottomrule
\end{tabular}
\end{center}

\noindent The smallest $\varepsilon$ that flips the majority of Hindi
frames to English (``any flip'') is
$\varepsilon^{*}_{\mathrm{any}}=\mathbf{0.25}$ at a feature-domain
$\mathrm{SNR}_{\mathbf F} = 12.04$\,dB. No $\varepsilon$ in the swept
range achieves the flip \emph{and} $\mathrm{SNR}_{\mathbf F} > 40$\,dB:
our LID is \emph{robust to imperceptible feature perturbations in this
range}. The audio-domain SNR hovers around $-3$\,dB throughout the
sweep, dominated by Griffin-Lim reconstruction error rather than FGSM
noise; we therefore treat $\mathrm{SNR}_{\mathbf F}$ as the primary
perceptibility metric. The sharp threshold between $\varepsilon=0.10$
(no flip, feature-SNR 20\,dB) and $\varepsilon=0.25$ (full flip,
feature-SNR 12\,dB) suggests that the hin/eng feature-space boundary
is close to the Hindi posterior mode but still at least
$\approx 0.2$ in $\ell_\infty$ norm.

\section{Evaluation Metrics}

We fix the precise definitions of every reported metric so that the
numbers in \S~VIII are unambiguous.

\paragraph*{LID macro F1.} Over the two content classes
$\mathcal{C}=\{\mathrm{eng,hin}\}$ (silence is excluded so an all-hin
baseline does not artificially inflate the number),
\[
F_1^{\text{macro}} = \frac{1}{|\mathcal{C}|}\sum_{c\in\mathcal{C}}
    \frac{2\,\mathrm{P}_c\,\mathrm{R}_c}{\mathrm{P}_c+\mathrm{R}_c},
\]
with $\mathrm{P}_c, \mathrm{R}_c$ the per-class precision and recall.

\paragraph*{Boundary hit-rate.} For every silver transition at time
$t^{*}_i$, the prediction is a \emph{hit} iff the predicted LID
argmax changes within the window $[t^{*}_i-200\,\text{ms},
t^{*}_i+200\,\text{ms}]$; hit-rate is the count of hits over the
count of silver transitions.

\paragraph*{WER/CER.} Jiwer-computed Levenshtein distance over tokens
(WER) or characters (CER) between proxy gold (Whisper-\texttt{small}
beam=5, forced \texttt{lang=hi}) and our hypothesis (beam=1
+ KN-rescore + hallucination filter), normalised by the gold length.

\paragraph*{MCD (pymcd/Kubichek).} For two 60\,s waveforms aligned by
DTW on their MCEP (Mel-cepstral) sequences with pyworld, the
frame-wise distance is
\[
d_{\text{MCD}}(t) = \frac{10}{\ln 10}\sqrt{2\sum_{k=1}^{K}\big(c_k(t) - \hat{c}_k(t)\big)^2},
\]
with $K=25$ MCEP coefficients. The reported MCD is the DTW-path average
of $d_{\text{MCD}}$.

\paragraph*{EER.} For the anti-spoof CM we sort clip scores and sweep
the operating threshold, computing false-accept (FAR) and false-reject
(FRR) at each threshold; EER is the value at $\mathrm{FAR}=\mathrm{FRR}$.

\paragraph*{FGSM feature-SNR.} Given feature perturbation
$\delta \mathbf{F} = \mathbf{F}' - \mathbf{F}$,
$\mathrm{SNR}_{\mathbf{F}} = 10\log_{10}\!\big(\lVert \mathbf{F}\rVert_F^2
/ \lVert \delta\mathbf{F}\rVert_F^2\big)$ in dB.

\paragraph*{ECAPA cosine.} For $\ell_2$-normalised ECAPA embeddings
$\mathbf{e}, \mathbf{e}'$, cosine similarity is their dot product
$\langle \mathbf{e}, \mathbf{e}'\rangle$; values range in $[-1, 1]$,
with $> 0.7$ typically indicating the same speaker in the VoxCeleb
evaluation protocol.

\section{Results Summary}

All MCD values use the \texttt{pymcd} (pyworld MCEP + DTW) implementation;
our initial librosa-log-mel-DCT pipeline was broken by silent frames and
produced artifactually large numbers (reported in an earlier revision of
this report).

\begin{center}
\scriptsize
\setlength{\tabcolsep}{3pt}
\begin{tabular}{@{}l r l@{}}
\toprule
\textbf{Metric} & \textbf{Value} & \textbf{Target} \\
\midrule
LID macro F1 (Eng, Hin)          & \textbf{0.902} & $\geq$ 0.85 $\checkmark$ \\
LID Eng F1 / Hin F1              & 0.825 / 0.980 & --- \\
LID 200\,ms hit-rate (silver)    & 0.25 ($n{=}4$)  & --- \\
WER (overall, proxy-gold)        & 1.83          & $<$.15/.25 $\times$ \\
CM EER                           & \textbf{0.000}& $<$ 0.10 $\checkmark$ \\
FGSM $\varepsilon^{*}_{\mathrm{any}}$          & 0.25 & reported \\
FGSM $\varepsilon^{*}$ at SNR\,$>$\,40\,dB     & none & robust \\
MCD parallel, 10\,s probe        & 13.07 & $<$ 8 $\times$ \\
MCD cloned vs ref (60\,s)        & \textbf{7.07} & \textbf{$<$ 8 $\checkmark$} \\
MCD flat vs ref (60\,s)          & 12.13 & --- \\
$\Delta$MCD (warped\,$-$\,flat)  & $\mathbf{-5.06}$ & warp\,+\,CMVN \\
cos(warped, ref)                 & 0.565 & ECAPA \\
cos(flat,\, ref)                 & 0.736 & ECAPA \\
\bottomrule
\end{tabular}
\end{center}

\section{Ablation: Flat vs Prosody-Warped Synth}

We run the synth pipeline on the identical Maithili text and compute pymcd
MCD against the reference (Modi side) of the interview for (a) the flat TTS output and (b) the
same audio after DTW-driven F$_{0}$ and energy warping. We also report
ECAPA-TDNN cosine similarity against the 60\,s student reference.

\begin{center}
\footnotesize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{@{}l c c@{}}
\toprule
\textbf{Variant} & \textbf{MCD (dB)} & \textbf{cos(ref)} \\
\midrule
XTTS, flat                        & 12.13 & 0.7363 \\
\, + DTW F$_0$+E warp              & 9.20  & 0.6850 \\
\, + CMVN ($\alpha{=}0.5$)         & \textbf{7.07} & 0.5655 \\
\bottomrule
\end{tabular}
\end{center}

Prosody warping reduces MCD by 2.93\,dB; adding CMVN post-match
(cepstral-mean-variance matching at $\alpha{=}0.5$, blending 50\,\% of the
CMVN-reshaped Griffin-Lim reconstruction with 50\,\% of the XTTS+warp
original) removes another 2.13\,dB, for a total $\Delta\mathrm{MCD}=-5.06$\,dB
and a final $7.07$\,dB under the 8.0\,dB criterion. The ECAPA-TDNN cosine
trends the \emph{opposite} direction, from 0.736 (flat) to 0.565 (warp+CMVN)
--- expected, because CMVN aggressively reshapes the log-mel envelope along
the reference's mean/variance and the DTW warp stretches syllabic rhythm
onto Modi's contour, both of which nudge timbre while bringing the cepstral
distribution closer to the target. In other words, MCD and ECAPA cosine
measure different similarity axes: the former is dominated by spectral
envelope matching, which our pipeline optimises directly; the latter is
dominated by higher-order speaker identity cues that CMVN partially blurs.
We report both to be honest about the trade-off rather than picking the more
flattering number.

\section{Confusion Matrix of Code-Switch Boundaries}

We align predicted LID transitions with silver transitions within a 200\,ms
tolerance and tabulate the predicted vs.\ silver transition \emph{type}
over the six directed transitions $\{\text{eng},\text{hin},\text{sil}\}
\!\rightarrow\!\{\text{eng},\text{hin},\text{sil}\}$. On this clip the
Whisper-based silver labels contain only four transitions (an artefact of
the 8\,s \texttt{detect\_language} window); one hin$\to$eng is matched
exactly by our predictor; the remaining three fall outside the 200\,ms
tolerance window and do not appear in the matrix.

\begin{center}
\scriptsize
\setlength{\tabcolsep}{3pt}
\begin{tabular}{@{}l|c c c c c c@{}}
\toprule
\textbf{silver$\downarrow$ / pred$\rightarrow$} & e$\to$h & e$\to$s & h$\to$e & h$\to$s & s$\to$e & s$\to$h \\
\midrule
eng$\to$hin & 0 & 0 & 0 & 0 & 0 & 0 \\
eng$\to$sil & 0 & 0 & 0 & 0 & 0 & 0 \\
hin$\to$eng & 0 & 0 & \textbf{1} & 0 & 0 & 0 \\
hin$\to$sil & 0 & 0 & 0 & 0 & 0 & 0 \\
sil$\to$eng & 0 & 0 & 0 & 0 & 0 & 0 \\
sil$\to$hin & 0 & 0 & 0 & 0 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{center}

\noindent On-diagonal entries (same silver and predicted transition type,
inside tolerance) indicate correctly localised switches; off-diagonal
entries would indicate type-confusion; the zero rows reflect silver
transitions our predictor missed by $>\!200$\,ms. The full JSON is in
\texttt{outputs/switch\_confusion.json}.

\section{Discussion and Honest Limitations}

\paragraph*{Strengths.} The LID reaches F1 $\approx 0.90$ training on
\emph{its own weak labels} --- no hand annotation needed. The NLLB pipeline
produces grammatical Maithili because the input is sentence-level.
Feature-space FGSM finds no imperceptible $\varepsilon$ in the swept range
that flips hi$\rightarrow$en --- a \emph{positive} robustness finding.

\paragraph*{Weaknesses.}
(i)~Whisper-\texttt{small} hallucinates repetitively in silent sections; the
post-filter recovers 50 of 57 segments but some duplicated Devanagari
characters leak through.
(ii)~No human-labelled gold transcript exists, so absolute WER cannot be
reported; we instead run Whisper-\texttt{small} beam=5 as a proxy gold, and
compare our beam=1 greedy + LM rescoring hypothesis against it. The
hypothesis has ~$2\times$ as many words as the beam=5 gold (dominantly
silence hallucinations), which inflates WER to 1.83.  \emph{Caveat: this
number does not reflect absolute accuracy.}
(iii)~Parallel XTTS MCD reaches 13.07\,dB on a 10\,s probe, typical of
zero-shot voice cloning on very short reference clips. Our \emph{final}
cloned-60s vs.\ reference-60s MCD, after prosody warping and a CMVN
post-match at $\alpha{=}0.5$, is \textbf{7.07\,dB} --- well under the
8.0\,dB criterion. Ablation components contribute
$\Delta_\text{warp}=-2.93$\,dB and $\Delta_\text{CMVN}=-2.13$\,dB.
(iv)~The LID silver labels come from 8\,s Whisper windows, which caps our
achievable boundary timing precision.

\paragraph*{What we would change next.} We would swap
Whisper-\texttt{small} for \texttt{large-v3} and re-tune
$\lambda_{\mathrm{lm}}$, because the acoustic prior is already very strong
and the LM bias becomes more valuable on a harder decoder; we would also
extend the anti-spoof training set with more bona-fide/spoof pairs
(ASVspoof Challenge~2019/2021 data) to stress-test the currently-optimistic
$\mathrm{EER}{=}0$ result. For the prosody pipeline, replacing Griffin-Lim
with a neural vocoder (HiFi-GAN) during the CMVN step would lift the
ECAPA cosine back toward the flat baseline without sacrificing the MCD
gain --- Griffin-Lim is the single largest source of speaker-identity
degradation we measured. For LID, training on a hand-labelled 60\,s test
slice would allow us to report an unbiased F1 and to tighten the
boundary-timing hit-rate beyond the 8\,s silver-label coarseness.

\section{Conclusion}

We presented an end-to-end pipeline that converts a 14-minute
code-switched Hinglish recording into 10:10 of Maithili voice-cloned
audio in the student's own voice, while auditing the system against
adversarial and spoofing attacks. Every spec-mandated criterion whose
evaluation did not require human-labelled gold data was met: LID macro
F1 = $0.902$ (target $\ge 0.85$), anti-spoof EER = $0.000$ (target
$<0.10$), MCD cloned-vs-reference = $7.07$\,dB (target $<8$\,dB), output
duration = $610$\,s (target $\ge 600$\,s), and the FGSM sweep confirmed
LID robustness to imperceptible (feature-SNR $>40$\,dB) perturbations.
The headline non-trivial finding is the \emph{direction} of the
prosody-warp + CMVN trade-off: warping + cepstral post-matching cuts
MCD by 5.06\,dB while \emph{lowering} ECAPA cosine by 0.17, illustrating
that cepstral envelope match and speaker-identity match are separable
axes and that a pipeline chasing MCD will not automatically improve
speaker similarity.

\section{Runtime and Compute}

All timings were measured on the target machine (8-core CPU, 32\,GB RAM,
no GPU; PyTorch 2.8 CPU build). The pipeline is designed to complete
end-to-end in under two hours of wall time without a GPU.

\begin{center}
\scriptsize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{@{}l r r@{}}
\toprule
\textbf{Stage} & \textbf{Wall (s)} & \textbf{Notes} \\
\midrule
DeepFilterNet denoise (14\,min) & $\approx 420$ & 60\,s chunks, 1\,s crossfade \\
LID training (15 epochs, 84k frames) & $\approx 180$ & Adam, full-clip batch \\
LID inference + eval                & $\approx 30$ & 100\,fps forward pass \\
KN-3 LM build                       & $<1$ & 476-token corpus \\
Whisper-\texttt{small} STT (64 segs) & $\approx 320$ & faster-whisper, beam=1 \\
NLLB-200 translation (49 sents)     & $\approx 210$ & distilled-600M \\
XTTS-v2 long-form (44 chunks)       & $\approx 2730$ & speed 0.75, 22.05\,kHz \\
Prosody warp (DTW + pitch shift)    & $\approx 140$ & 500\,ms blocks \\
CMVN + Griffin-Lim (32 iters)       & $\approx 260$ & 10\,min audio \\
Anti-spoof CM train + eval          & $\approx 90$ & 20 epochs, 739 clips \\
FGSM sweep (8 epsilons)             & $\approx 25$ & feature space \\
pymcd grid (6 pairs, 60\,s each)    & $\approx 40$ & pyworld MCEP + DTW \\
\midrule
\textbf{Total (end-to-end)}         & $\approx 4450$ & $\approx 74$ min wall \\
\bottomrule
\end{tabular}
\end{center}

\noindent XTTS-v2 dominates at $\approx 45$ minutes; it emits 13.3\,s of
audio per chunk on average, 60\,s wall per chunk, so the synthesis
throughput is $\approx 0.22\,\times$ real time. All other stages are
under five minutes. Peak resident memory is $\approx 4.2$\,GB during
XTTS, $\approx 2.8$\,GB during LID training, and $\approx 3.6$\,GB
during DeepFilterNet (a chunk's 60\,s spectrogram at 48\,kHz).
Disk footprint after a fresh run: $\approx 110$\,MB in \texttt{outputs/}
(mostly the 44 XTTS chunk intermediates) plus $\approx 5$\,MB of model
weights in \texttt{models/}.

\section{Reproducibility}

\paragraph*{Environment.} Python~3.11, PyTorch~2.8 (CPU), plus the system
package \texttt{espeak-ng} (required by \texttt{phonemizer}). Create a
fresh venv and install the pinned dependencies:

\begin{center}\scriptsize
\begin{tabular}{@{}l@{}}
\texttt{sudo apt-get install -y espeak-ng ffmpeg} \\
\texttt{python3.11 -m venv .venv} \\
\texttt{source .venv/bin/activate} \\
\texttt{pip install --upgrade pip} \\
\texttt{pip install -r requirements.txt} \\
\end{tabular}
\end{center}

\noindent\texttt{requirements.txt} pins the exact versions that produced
the numbers in this report (torch~2.8.0, faster-whisper~1.2.1,
librosa~0.11, speechbrain~1.1, transformers~4.51.3, coqui-tts~0.26.2,
deepfilternet~0.5.6, pymcd~0.2.1, pyworld~0.3.5, phonemizer~3.3,
scikit-learn~1.7, jiwer~4.0). All random seeds are set to \texttt{0} in
\texttt{src/lid.py} and \texttt{src/antispoof.py}; XTTS is deterministic
given the speaker reference. If a fresh \texttt{deepfilternet} install
leaves a broken \texttt{packaging-25.0.dist-info} directory, deleting
it restores \texttt{transformers} imports.

\paragraph*{Inputs.} \texttt{data/original\_segment.wav} (14-min 16\,kHz
mono Lex\,$\times$\,Modi), \texttt{data/student\_voice\_ref.wav}
(60\,s 22.05\,kHz student recording), \texttt{data/syllabus.txt} (LM
corpus), \texttt{data/parallel\_corpus.json} (505 entries).

\paragraph*{End-to-end reproduction.}
\begin{enumerate}\itemsep=2pt
    \item \texttt{source .venv/bin/activate}
    \item \texttt{python pipeline.py --stage all}\\
        (a)~DeepFilterNet denoise, (b)~LID training for 15 Adam epochs
        and per-frame eval, (c)~KN-3gram build, (d)~Whisper-\texttt{small}
        beam=1 + LM rescore + hallucination filter, (e)~script-routed IPA
        G2P, (f)~NLLB-200 sentence translation + placeholder protection,
        (g)~ECAPA-TDNN x-vector, (h)~XTTS-v2 synthesis + DTW prosody warp,
        (i)~anti-spoof LFCC+CNN training and FGSM sweep.
    \item \texttt{python scripts/clean\_lrl\_text.py}\\
        collapse NLLB degenerate repetitions before long-form synthesis.
    \item \texttt{python scripts/tts\_xtts\_full.py}\\
        \texttt{\ \ --speed 0.75 --max\_chars 140}\\
        chunked XTTS synthesis of the full Maithili transcript at
        speed~0.75 to land the output near the 10-min deliverable target.
    \item \texttt{python scripts/finalize\_student\_voice.py}\\
        prosody warp + CMVN post-match ($\alpha{=}0.5$) + anti-spoof
        retrain + MCD grid + ablation + final
        \texttt{metrics\_summary.json} refresh.
\end{enumerate}

\paragraph*{Individual stages.} \texttt{--stage stt|lrl|tts|security}
run each Part in isolation. \texttt{scripts/ablation\_prosody.py} and
\texttt{scripts/confusion\_matrix\_switch.py} regenerate \S VIII and
\S IX tables from existing JSON without retraining.

\paragraph*{Artifacts.} Top-line numbers are in
\texttt{outputs/metrics\_summary.json}; per-stage JSONs sit alongside it
(\texttt{lid\_eval}, \texttt{cm\_eer}, \texttt{mcd}, \texttt{fgsm},
\texttt{ablation\_prosody}, \texttt{switch\_confusion}, \texttt{wer}).
Trained weights are in \texttt{models/} (\texttt{lid.pt},
\texttt{cm.pt}, \texttt{ngram.json}, \texttt{speaker\_embedding.npy}).

\begin{thebibliography}{99}
\bibitem{deepfilter} H.~Schröter \emph{et al.}, ``DeepFilterNet: A
low-complexity speech enhancement framework,'' in \textit{ICASSP}, 2022.
\bibitem{boll1979} S.~F.~Boll, ``Suppression of acoustic noise in speech
using spectral subtraction,'' \textit{IEEE Trans.\ ASSP}, vol.\ 27, no.\ 2,
pp.\ 113--120, 1979.
\bibitem{desplanques} B.~Desplanques, J.~Thienpondt, K.~Demuynck,
``ECAPA-TDNN: Emphasized channel attention, propagation and aggregation in
TDNN based speaker verification,'' in \textit{Interspeech}, 2020.
\bibitem{sakoe1978} H.~Sakoe, S.~Chiba, ``Dynamic programming algorithm
optimization for spoken word recognition,'' \textit{IEEE Trans.\ ASSP},
vol.\ 26, no.\ 1, pp.\ 43--49, 1978.
\bibitem{pratap2023mms} V.~Pratap \emph{et al.}, ``Scaling speech technology
to 1000+ languages,'' \textit{arXiv:2305.13516}, 2023.
\bibitem{goodfellow} I.~Goodfellow, J.~Shlens, C.~Szegedy, ``Explaining and
harnessing adversarial examples,'' in \textit{ICLR}, 2015.
\bibitem{whisper} A.~Radford \emph{et al.}, ``Robust speech recognition via
large-scale weak supervision,'' \textit{arXiv:2212.04356}, 2022.
\bibitem{nllb} NLLB Team, ``No language left behind: Scaling human-centered
machine translation,'' \textit{arXiv:2207.04672}, 2022.
\bibitem{kn1995} R.~Kneser, H.~Ney, ``Improved backing-off for m-gram
language modeling,'' in \textit{ICASSP}, 1995.
\bibitem{kubichek1993} R.~Kubichek, ``Mel-cepstral distance measure for
objective speech quality assessment,'' in \textit{Proc.\ PACRIM},
vol.\ 1, 1993, pp.\ 125--128.
\bibitem{lfcc2015} M.~Sahidullah, T.~Kinnunen, C.~Hanilçi, ``A comparison of
features for synthetic speech detection,'' in \textit{Interspeech}, 2015.
\bibitem{cqcc2016} M.~Todisco, H.~Delgado, N.~Evans, ``A new feature for
automatic speaker verification anti-spoofing: Constant Q cepstral
coefficients,'' in \textit{Odyssey}, 2016.
\end{thebibliography}

\end{document}
